Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-15 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
Same day association, function, table and plot.

>>>>

*Note from Jingyang on Nov 14:*
*Just a little improvement advice for plot: Because the number (which labels the last disease's odds ratio) can only be seen one digital, I suggest to add more margin to the right side. Also for the DLM graph.*

```{r same day association fuction}
same_day_fun <- function(data, pm_df, temp_df){

  # limit to complete cases
  complete_data <- data %>% 
    # filter to complete case for smoke
    filter(!is.na(geo_smk_pm_zip))

  # output matrix of gwr values
  pm_matrix <- complete_data %>% 
    select(geo_smk_pm_zip) %>%
    # divide exposure values by 10 units to interpret on 10 ug/m^3 scale
    mutate_all(funs(./10)) %>% 
    # convert to matrix
    as.matrix()

  # output temp matrix
  temp_matrix <- complete_data %>% 
    select(wrf_temp_zip) %>%
    # convert to matrix
    as.matrix()

  # fit model with basis ----
  mod <- clogit(outcome ~ pm_matrix + temp_matrix + strata(personkey),
    data = complete_data)

  # odds ratio
  sd_estimates <- round(exp(summary(mod)$coefficient[1,1]), 3) # sd stands for same day

  # 95% lower bound
  sd_lower <- round(exp((summary(mod)$coefficient[1,1]) -
                                    1.96*(summary(mod)$coefficient[1,3])), 3)
  # 95% upper bound
  sd_upper <- round(exp((summary(mod)$coefficient[1,1]) +
                                    1.96*(summary(mod)$coefficient[1,3])), 3)
  # standard error
  sd_stderr <- round(summary(mod)$coefficient[1,3], 4)
  # p val
  sd_pvalue <- round(summary(mod)$coefficient[1,5], 4)

  return_estimate <- data_frame(sd_estimates, sd_lower, sd_upper) 
  return(return_estimate) 
} 
```

```{r same day association table}
sameday_cumulative_results <- outcome_df_list %>% 
  map_dfr(~same_day_fun(., pm_df=3, temp_df=2)) %>% 
  bind_cols(., data_frame(outcome_names)) %>% 
  select(outcome_names, sd_estimates, sd_lower, sd_upper) %>% 
  # preserve order of names
  mutate(outcome_names = parse_factor(outcome_names, levels = outcome_names))

knitr::kable(sameday_cumulative_results, 
  caption = "Same day odds ratio and CI of pharmacy/ED/urgent care visits")
```

```{r same day association graph}
# ggplot ----
plot <- ggplot(sameday_cumulative_results, aes(x=outcome_names, y = sd_estimates)) +
  geom_point(colour = "darkblue") +
  geom_text(aes(label = round(sd_estimates,2)), hjust = -0.25) +
  geom_errorbar(aes(ymin=sd_lower, ymax=sd_upper), 
                colour= "darkblue", width = 0.2) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  theme(
   panel.background = element_rect(fill = 'white', colour = 'black'),
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(),
   axis.text.x = element_text(angle=90, hjust = 1)) +
  ylab(expression("Same day odds ratio: 10 ug/m^3 increase smoke PM"[2.5])) +
  xlab("Outcomes")
